\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-11 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
moved the Stacey parameters to after the PML parameters in the Par_file, since using CPML is much better

@@

layers (see the options below) and leave this flag to \texttt{.false.}.

@@

\item [{\texttt{PML\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.} to turn on C-PML boundary conditions on the top surface which by default constitutes a free surface of the model.
\item [{\texttt{f0\_FOR\_PML}}] Determines the dominant frequency that will be used in the calculation of: \\ ALPHA\_MAX\_PML = PI*f0\_FOR\_PML.

>>>>

\item [{\texttt{PML\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.} to turn on C-PML boundary conditions on the top surface
instead of the usual free surface.
\item [{\texttt{f0\_FOR\_PML}}] Determines the dominant frequency that will be used in the calculation of PML damping profiles; this should be
set to the same (or similar) dominant frequency as that of the source that you will use in your simulation. If you plan to use a Dirac source,
then use the dominant frequency of the source wavelet with which you plan to convolve your seismograms later on in post-processing.

@@

layers (see the options above) and leave this flag to \texttt{.false.}.

@@
